Experiences Gamifying Developer Adoption\\ of Practices and Tools

### 2014-03-17 paper_id51.tex
cleanup and final license updates

% --- Author Metadata here ---
\conferenceinfo{ICSE}{'14, May 31 -- June 7, 2014, Hyderabad, India}
\CopyrightYear{is held by the owner/author(s). Publication rights licensed to ACM.}
\crdata{978-1-4503-2768-8/14/06}

@@

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\balance
\bibliography{mousetap} 
 % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%

>>>>

% --- Author Metadata here ---
\permission{Permission to make digital or hard copies of all or part of this work for personal or classroom use is granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page. Copyrights for components of this work owned by others than the author(s) must be honored. Abstracting with credit is permitted. To copy otherwise, or republish, to post on servers or to redistribute to lists, requires prior specific permission and/or a fee. Request permissions from Permissions@acm.org.}
\conferenceinfo{ICSE}{'14, May 31 -- June 7, 2014, Hyderabad, India}
\CopyrightYear{is held by the owner/author(s). Publication rights licensed to ACM.}
\crdata{978-1-4503-2768-8/14/06}

@@

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\balance
%\bibliography{mousetap} 
 % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
\begin{thebibliography}{10}

\bibitem{2013Oxford}
{\em {Oxford Dictionaries Online - American English (US)}}.
\newblock Oxford University Press, 2013.

\bibitem{Beecham2008Motivation}
S.~Beecham, N.~Baddoo, T.~Hall, H.~Robinson, and H.~Sharp.
\newblock {Motivation in Software Engineering: A Systematic Literature Review}.
\newblock {\em Inf. Softw. Technol.}, 50(9-10):860--878, Aug. 2008.

\bibitem{Coman2009Casestudy}
I.~D. Coman, A.~Sillitti, and G.~Succi.
\newblock {A Case-study on Using an Automated In-process Software Engineering
  Measurement and Analysis System in an Industrial Environment}.
\newblock In {\em International Conference on Software Engineering, ICSE},
  pages 89--99. IEEE, May 2009.

\bibitem{Dubois2013Understanding}
D.~J. Dubois and G.~Tamburrelli.
\newblock {Understanding Gamification Mechanisms for Software Development}.
\newblock In {\em Foundations of Software Engineering}. ACM, 2013.

\bibitem{Hall2009WEKA}
M.~Hall, E.~Frank, G.~Holmes, B.~Pfahringer, P.~Reutemann, and I.~H. Witten.
\newblock {The WEKA Data Mining Software: An Update}.
\newblock {\em SIGKDD Explorations}, 11(1), 2009.

\bibitem{wbsnipes:Hamari2011Framework}
J.~Hamari and V.~Eranti.
\newblock {Framework for Designing and Evaluating Game Achievements}.
\newblock In {\em Digra Conference}, Sept. 2011.

\bibitem{RefWorks:118}
T.~Hill and P.~Lewicki.
\newblock {\em {Statistics: Methods and Applications}}.
\newblock StatSoft, Inc, 2007.

\bibitem{V:Johnson2007Automated}
P.~M. Johnson and H.~Kou.
\newblock {Automated Recognition of Test-Driven Development with Zorro}.
\newblock In {\em Agile Conference (AGILE)}, pages 15--25. IEEE, Aug. 2007.

\bibitem{Kou2010Operational}
H.~Kou, P.~Johnson, and H.~Erdogmus.
\newblock {Operational Definition and Automated Inference of Test-driven
  Development with Zorro}.
\newblock {\em Automated Software Engineering}, 17(1):57--85, 2010.

\bibitem{wbsnipes:MaehrCulture}
M.~Maehr.
\newblock {Culture and Achievement Motivation.}
\newblock {\em American Psychologist}, 1974(29):887--896, 1974.

\bibitem{Moser2008Case}
R.~Moser, P.~Abrahamsson, W.~Pedrycz, A.~Sillitti, and G.~Succi.
\newblock {A Case Study on the Impact of Refactoring on Quality and
  Productivity in an Agile Team}.
\newblock In B.~Meyer and et~al., editors, {\em Balancing Agility and Formalism
  in Software Engineering}, volume 5082 of {\em Lecture Notes in Comp. Sci.},
  pages 252--266. Springer], 2008.

\bibitem{Moser2006Does}
R.~Moser, A.~Sillitti, P.~Abrahamsson, and G.~Succi.
\newblock {Does Refactoring Improve Reusability?}
\newblock In M.~Morisio, editor, {\em Reuse of Off-the-Shelf Components},
  volume 4039 of {\em Lecture Notes in Comp. Sci.}, pages 287--297. Springer
  Berlin Heidelberg, 2006.

\bibitem{MurphyHill2012Improving}
E.~Murphy-Hill, R.~Jiresal, and G.~C. Murphy.
\newblock {Improving Software Developers' Fluency by Recommending Development
  Environment Commands}.
\newblock In {\em Foundations of Software Engineering}. ACM, Nov. 2012.

\bibitem{wbsnipes:Hill2011Peer}
E.~Murphy-Hill and G.~C. Murphy.
\newblock {Peer Interaction Effectively, Yet Infrequently, Enables Programmers
  to Discover New Tools}.
\newblock In {\em ACM Conference on Computer supported cooperative work}, CSCW.
  ACM, 2011.

\bibitem{V:MurphyHill2012How}
E.~Murphy-Hill, C.~Parnin, and A.~P. Black.
\newblock {How We Refactor, and How We Know It}.
\newblock {\em IEEE Transactions on Software Engineering}, 38:5--18, Jan. 2012.

\bibitem{Rcitation}
{R Core Team}.
\newblock {\em R: A Language and Environment for Statistical Computing}.
\newblock R Foundation for Statistical Computing, Vienna, Austria, 2013.

\bibitem{wbsnipes:Robillard2004How}
M.~P. Robillard, W.~Coelho, and G.~C. Murphy.
\newblock {How Effective Developers Investigate Source Code: an Exploratory
  Study}.
\newblock {\em IEEE Transactions on Software Engineering}, 30:889--903, Dec.
  2004.

\bibitem{wbsnipes:SaatchiGameification}
{Saatchi and Saatchi S}.
\newblock Gameification for business brands and loyalty, June 2011.

\bibitem{Shepherd2012Sando}
D.~Shepherd, K.~Damevski, B.~Ropski, and T.~Fritz.
\newblock {Sando: an Extensible Local Code Search Framework}.
\newblock In {\em Foundations of Software Engineering}. ACM, 2012.

\bibitem{Singer2013a}
L.~Singer.
\newblock {\em {I}mproving the {A}doption of {S}oftware {E}ngineering
  {P}ractices {T}hrough {P}ersuasive {I}nterventions}.
\newblock PhD thesis, Gottfried Wilhelm Leibniz Universität Hannover, 2013.

\bibitem{Singer2012It}
L.~Singer and K.~Schneider.
\newblock {It was a Bit of a Race: Gamification of Version Control}.
\newblock In {\em Second International Workshop on Games and Software
  Engineering: Realizing User Engagement with Game Engineering Techniques
  (GAS)}. IEEE, June 2012.

\bibitem{Snipes2013Towards}
W.~Snipes, V.~Augustine, A.~R. Nair, and E.~M. Hill.
\newblock {Towards Recognizing and Rewarding Efficient Developer Work
  Patterns}.
\newblock In {\em International Conference on Software Engineering}, ICSE.
  IEEE, 2013.

\end{thebibliography}
